Supplementary information for: Carbon stocks in aboveground biomass for Colombian mangroves with associated uncertainties

### 2017-05-22 Supplementary information.tex
in supplementary information all models were updated and modification in methods in article
Edited supplementary information

\documentclass[review, authoryear]{elsarticle}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\usepackage{pdflscape}
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amssymb, amsmath}
\usepackage{topcapt}
%\usepackage[round]{natbib}
\usepackage{booktabs}
\usepackage{subscript}
\usepackage{textcomp}

@@

\title{Supplementary information}
\author[MPI,CYB]{Jhoanata M. Bolivar}
\author[MPI,CYB]{Carlos A. Sierra}
\address[MPI]{Max Planck Institute for Biogeochemistry, Hans-Kn\"oll-Str. 10, 07745 Jena, Germany}
\address[CYB]{Research Center on Ecosystems and Global Change Carbono \& Bosques, Medell\'in, Colombia}

@@

@@

   \topcaption{Above ground biomass (AGB) data sources used to estimation of total AGB carbon stock in Colombian mangroves and development of predictive models.} % requires the topcapt package

@@

  \topcaption {Statistical regression models for AGB. When log is the natural logarithm; AGB is the above ground biomass (Mg/ha); BIO9 is the mean temperature of driest quarter (\textcelsius); BIO10 mean temperature of warmest quarter (\textcelsius); BIO11 mean temperature of coldest quarter (\textcelsius); BIO16 is the precipitation of the wettest quarter (mm); EVI is the enhanced vegetation index; Lat is the absolute value of latitude (decimal degrees);  n is the number of observations; R$_a^2$  is the adjusted coefficient of determination; MSE is the mean squared error; F is the F-statistic calculated; AIC is the akaike information criterion }  % requires the topcapt package

@@

       Model  & n & R$_{a}^{2}$ & MSE & F & AIC\\

@@

    $(1)AGB=-2.210$^{e+03}$+2.946\$^{e+00}$BIO10+4.687$^{e+00}$BIO11+2.108${e-01}$BIO16-2.334$^{e-01}$BIO17+2.465$^{e+02}$EVI$&40&0.04163 &4157&1.34&\\
    $(2)AGB=-1.876$^{e+03}$+7.766$^{e+00}$BIO1+7.64$^{e-02}$BIO4+5.413$^{e-03}$BIO12-2.908$^{e-00}$BIO15$&43&-0.0278&4338&0.72&\\
    $(3)AGB=-3.260$^{e+03}$+1.233$^{e+01}$BIO1+1.61$^{e-01}$BIO4+1.934$^{e-02$}BIO12-3.805$^{e+00}$BIO15+2.835$^{e+02}$EVI$&40&0.07695&4003&1.65&\\    
    $(4)AGB=-1.920$^{e+03}$-7.292$^{e+01}$Lat+7.878$^{e+00}$BIO10+1.846$^{e+00}$BIO11-1.115$^{e-01}$BIO16+2.404$^{e-02}$BIO17+1.561$^{e-02}$EVI$&40&0.1288&3779&1.961&\\   
    $(5)AGB=-1.372$^{e+03}$+6.358$^{e+00}$BIO10+1.789$^{e+00}$BIO11-7.389$^{e-02}$BIO16-1.229$^{e-01}$BIO17-7.746$^${e+01}Lat$&43&0.154&3571&2.529&\\   
    $(6)AGB=-1.286$^{e+03}$-9.594$^{e+01}$Lat+8.621$^{e+00}$BIO1+1.161$^{e-01}$BIO4-6.145$^{e-02}$BIO12-4.687$^{e-01}$BIO15$&43&0.1819&3453&2.868&\\    
$(7)AGB=-2.219$^{e+03}$-7.703$^{e+01}$Lat+1.113$^{e+00}$BIO1+1.885$^{e-01}$BIO4-4.071$^{e-02}$BIO12-1.735$^{e-01}$BIO15+1.813$^{e+02}$EVI$&41&0.1762&3573&2.39&\\
$(8)AGB=35338.8860-155.9330|Lat|-2490.0405\frac{BIO1}{10}+49.1282(\frac{BIO1}{10})^2-85.6399\frac{BIO11}{10}-0.1171BIO12+0.4483BIO15$&43&0.1975&3387&2.72&479.88247\\
$(9)AGB=60064.4482-127.7343|Lat|-4376.4264\frac{BIO1}{10}+81.8955(\frac{BIO1}{10})^2-17.3961\frac{BIO11}{10}-0.1014BIO12+1.9823BIO15+320.5646EVI$&41&0.2835&3046&3.26&454.33614\\
$(10)AGB=-1916.5321+7.3424BIO9+0.1126BIO17$&43&0.1456&3607&4.58&479.11018\\
$(11)AGB=-1.693$^{e+03}$-2.897$^{e+01}$Lat+7.567$^{e+00}$BIO9-4.108$^{e-02}$BIO17$&43&0.2072&3346&4.66&476.80085\\
$(12)AGB=-1.485$^{e+03}$-1.662$^{e+00}$Lat+5.443$^{e+00}$BIO9+5.658$^{e-02}$BIO17+2.770$^{e+02}$EVI$&41&0.2755&3080&4.80&452.36112\\
$(13)AGB=-1368.411-11.799Lat+5.451BIO9+231.860EVI$&41&0.2889&3023&6.42&450.71764\\
$(14)AGB=-716.047+2.522BIO9+335.402EVI$&41&0.2713&3098&8.44&450.81526\\
$(15)AGB=-1860.211+7.958BIO9-22.944Lat$&43&0.2225&3282&7.01&475.05212\\
$(16)AGB=-423.235+1.943BIO9$&43&0.01697&4149&1.72&484.20182\\
$(17)AGB=-856.79518-6.53917BIO11+0.01171BIO16+9.62033BIO9+200.26658EVI$&41&0.2859&3036&5.00&451.76863\\
$(18)AGB=-1364.4334+4.8624BIO11+0.0324BIO16+358.2106EVI$&46&0.2492&3192&5.42&452.94654\\
$(19)AGB=-822.9927+3.0227BIO11+0.2433BIO16-0.4077BIO17$&43&0.04791&4019&1.70&484.67591\\
$(20)AGB=-319.78271-13.78940BIO11-0.00399BIO16+9.78050BIO9+4.98395BIO1+231.90575EVI$&41&0.2792&3064&4.10&452.99699\\
$(21)AGB=4.173$^{e+04}$-1.606$^{e+02}$\frac{BIO11}{10}-4.733$^{e-02}$BIO16+1.602$^{e+02}$\frac{BIO9}{10}-3.083$^{e+03}$\frac{BIO1}{10}+5.685$^{e+01}$(\frac{BIO1}{10})^2+2.826$^{e+02}$EVI$&41&0.3096&2935&3.99&452.03760\\
$(22)AGB=-3.485$^{e+02}$+1.954$^{e-03}$BIO10^2+3.104$^{e-03}$BIO11^2-6.339$^{e-05}$BIO16^2+3.609$^{e-04}$BIO17^2+5.595$^{e+02}$EVI^2$&41&0.233&3261&3.43&455.54124\\
$(23)\log{AGB}=-54.802662+5.751671\log{BIO10}+5.097236\log{BIO11}-0.003928\log{BIO16}-0.004322\log{BIO17}+1.691458\log{EVI}$&41&0.2164&0.585&3.21&101.88486\\
$(24)AGB=-3301.918+718.549\log{BIO10}-122.657\log{BIO11}+30.615\log{BIO16}-6.271\log {BIO17}+131.200\log{EVI}$&41&0.2008&3397&3.01&457.22750\\
$(25)\log{AGB}=-100.7499+18.7172\log{BIO9}+0.2023\log{BIO16}+1.1821\log{EVI}$&41&0.3038&0.520&6.82&95.31651\\
$(26)\log{AGB}=-25.6202+12.1786\log{BIO9}-4.1606\log{BIO16}+0.9976\log{EVI}-1.1664|Lat|$&41&0.3777&0.465&7.07&91.59005\\
$(27)\log{AGB}=26.5733+29.8163\log{BIO9}-3.8958\log{BIO16}+0.7998\log{EVI}-0.9563|Lat|-27.7092\log{BIO11}$&41&0.3701&0.470&5.70&92.93683\\ 
$(28)AGB=1098.74-284068.51\frac{1}{BIO9}+35004.17\frac{1}{BIO16}-36.37\frac{1}{EVI}+713.59\frac{1}{|Lat|}$&41&0.256&3163&4.44&453.44744\\
$(29)\frac{1}{AGB}=1.763$^{e-01}$-6.966$^{e-04}$BIO9+3.451$^{e-05}$BIO16-1.008$^t{e-01}$EVI+5.315$^{e-03}$|Lat|$&41&0.1325&0.0014&2.53&-147.62232\\
$(30)\frac{1}{AGB}=-0.12246+28.07379\frac{1}{BIO9}-10.38792\frac{1}{BIO16}+0.01322\frac{1}{EVI}+0.18235\frac{1}{|Lat|}$&41&0.0917&0.0014&2.01&-145.73673\\
$(31)\log{AGB}=55.0753+0.3973\log{BIO9}-5.0320\log{BIO16}+2.0524\log{EVI}-8.5249\log{|Lat|}$&41&0.3756&0.466&7.01&91.73306\\
$(32)\log{AGB}=-1.615$^{e+01}$+7.970$^{e-02}$\log{BIO9}-3.738$^{e-04}$\log{BIO16}+2.816$^{e+00}$\log{EVI}-2.259$^{e-01}$|Lat|$&41&0.3193&0.508&5.69&95.26750\\
$(33)AGB=2577.5+186.7\log{BIO9}-325.0\log{BIO16}+142.5\log{EVI}-593.8\log{|Lat|}$&41&0.3223&2881&5.76&449.62118\\
$(34)AGB=-2541.15+178.36\sqrt{BIO9}-2.78\sqrt{BIO16}+259.48\sqrt{EVI}-130.84\sqrt{|Lat|}$&41&0.2699&3104&4.70&452.67672\\
$(35)\sqrt{AGB}=-7.719$^{e+01}$+3.201$^{e-01}$BIO9-7.403$^{e-05}$BIO16+1.253$^{e+01}$EVI-5.965$^{e-01}$|Lat|$&41&0.3357&7.53&6.05&205.81366\\
$(36)\log{AGB}=20.8619-4507.8468\frac{1}{BIO9}+324.2172\frac{1}{BIO16}-0.4312\frac{1}{EVI}+5.6351\frac{1}{|Lat|}$&41&0.2717&0.544&4.73&98.04207\\ 
$(37)AGB=-1368.411+5.451BIO9+231.860EVI-11.799|Lat|$&41&0.2889&3023&6.42&450.71764\\
$(38)\log{AGB}=-107.9639+20.4502\log{BIO9}+1.1227\log{EVI}-0.5814\log{|Lat|}$&41&0.313&0.513&7.07&94.76887\\
$(39)\log{AGB}=-16.91915+0.07633BIO9+3.28301EVI-0.09007|Lat|$&41&0.3323&0.499&7.63&93.60484\\
$(40)AGB=-7953.94+1482.05\log{BIO9}+82.41\log{EVI}-80.71\log{|Lat|}$&41&0.2824&3050&6.25&451.08829\\ 
$(41)AGB=-2854.91+179.82\sqrt{BIO9}+280.77|sqrt{EVI}-62.46\sqrt{|Lat|}$&41&0.2874&3029&6.38&450.80450\\
$(42)\sqrt{AGB}=-77.3401+0.3194BIO9+12.6178EVI-0.5696|Lat|$&41&0.3536&7.330&8.30&203.81456\\
$(43)\log{AGB}=25.4963-5632.1520\frac{1}{BIO23}-0.3299\frac{1}{EVI}+3.7667\frac{1}{|Lat|}$&41&0.2848&0.534&6.31&96.42112\\
$(44)\log{AGB}=20.4877-4101.9051\frac{1}{BIO9}-0.3843\frac{1}{EVI}$ &41&0.2862&0.533&9.02&95.43342\\
$(45)\log{AGB}=-74.413+14.816\log{BIO9}+1.338\log{EVI}$&41&0.3181&0.509&10.33&93.56169\\
$(46)\log{AGB}=-11.93921+0.05398BIO9+4.07342EVI$&41&0.3378&0.494&11.20&92.35835\\
$(47)\sqrt{AGB}=-45.8449+0.1781BIO9+17.6167EVI$&41&0.3389&7.50&11.25&203.83289\\   
$(48)\log{AGB}=21.9702-4494.1151\frac{1}{BIO9}-67.5181\frac{1}{BIO16}-0.3576\frac{1}{EVI}$ &41&0.2674&0.547&5.866&97.40678\\

@@

>>>>

\documentclass[authoryear]{elsarticle}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\usepackage{pdflscape}
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amssymb, amsmath}
\usepackage{topcapt}
%\usepackage[round]{natbib}
\usepackage{booktabs}
\usepackage{subscript}
\usepackage{textcomp}

@@

\title{Supplementary information for: Carbon stocks in aboveground biomass for Colombian mangroves with associated uncertainties}
\author[MPI,CYB]{Jhoanata M. Bolivar}
\author[TU,CYB]{Victor H. Gutierrez-Velez}
\author[MPI,CYB]{Carlos A. Sierra}
\address[MPI]{Max Planck Institute for Biogeochemistry, Hans-Kn\"oll-Str. 10, 07745 Jena, Germany}
\address[CYB]{Research Center on Ecosystems and Global Change Carbono \& Bosques, Medell\'in, Colombia}
\address[TU]{Department of Geography and Urban Studies, Temple University, Philadelphia, PA 19122, USA}

@@

This supplementary material contains two tables. The first table presents all sources of information on AGB density used for estimation of national C stocks and model development. The second table presents all the statistical models tested in our analysis with corresponding results from statistical tests.

@@

   \topcaption{Data sources of Aboveground biomass (AGB) used to estimation of total AGB carbon stock in Colombian mangroves and development of predictive models.} % requires the topcapt package

@@

  \topcaption {Statistical regression models tested in our analysis. AGB represents aboveground biomass (Mg/ha); BIO9 is the mean temperature of driest quarter (\textcelsius); BIO10 mean temperature of warmest quarter (\textcelsius); BIO11 mean temperature of coldest quarter (\textcelsius); BIO16 is the precipitation of the wettest quarter (mm); EVI is the enhanced vegetation index; Lat is the absolute value of latitude (decimal degrees);  n is the number of observations; R\textsubscript{a}\textsuperscript{2} is the adjusted coefficient of determination; MSE is the mean squared error; F is the F-statistic calculated; AIC is Akaike's information criterion }  % requires the topcapt package

@@

       Model  & n & R\textsubscript{a}\textsuperscript{2} & MSE & F & AIC\\

@@

    $(1)AGB=-2.210\textsuperscript{e+03}+2.946\textsuperscript{e+00}BIO10+4.687\textsuperscript{e+00}BIO11+2.108\textsuperscript{e-01}BIO16-2.334\textsuperscript{e-01}BIO17+2.465\textsuperscript{e+02}EVI$&40&0.04163 &4157&1.34&454.313\\
    $(2)AGB=-1.876\textsuperscript{e+03}+7.766\textsuperscript{e+00}BIO1+7.64\textsuperscript{e-02}BIO4+5.413\textsuperscript{e-03}BIO12-2.908\textsuperscript{e-00}BIO15$&43&-0.0278&4338&0.72&488.850\\
    $(3)AGB=-3.260\textsuperscript{e+03}+1.233\textsuperscript{e+01}BIO1+1.61\textsuperscript{e-01}BIO4+1.934\textsuperscript{e-02}BIO12-3.805\textsuperscript{e+00}BIO15+2.835\textsuperscript{e+02}EVI$&40&0.07695&4003&1.65&452.811\\    
    $(4)AGB=-1.920\textsuperscript{e+03}-7.292\textsuperscript{e+01}Lat+7.878\textsuperscript{e+00}BIO10+1.846\textsuperscript{e+00}BIO11-1.115\textsuperscript{e-01}BIO16+2.404\textsuperscript{e-02}BIO17+1.561\textsuperscript{e-02}EVI$&40&0.1288&3779&1.961&451.303\\   
    $(5)AGB=-1.372\textsuperscript{e+03}+6.358\textsuperscript{e+00}BIO10+1.789\textsuperscript{e+00}BIO11-7.389\textsuperscript{e-02}BIO16-1.229\textsuperscript{e-01}BIO17-7.746\textsuperscript{e+01}Lat$&43&0.154&3571&2.529&481.333\\   
    $(6)AGB=-1.286\textsuperscript{e+03}-9.594\textsuperscript{e+01}Lat+8.621\textsuperscript{e+00}BIO1+1.161\textsuperscript{e-01}BIO4-6.145\textsuperscript{e-02}BIO12-4.687\textsuperscript{e-01}BIO15$&43&0.1819&3453&2.868&479.891\\    
$(7)AGB=-2.219\textsuperscript{e+03}-7.703\textsuperscript{e+01}Lat+1.113\textsuperscript{e+00}BIO1+1.885\textsuperscript{e-01}BIO4-4.071\textsuperscript{e-02}BIO12-1.735\textsuperscript{e-01}BIO15+1.813\textsuperscript{e+02}EVI$&41&0.1762&3573&2.39&449.069\\
$(8)AGB=35338.8860-155.9330|Lat|-2490.0405\frac{BIO1}{10}+49.1282(\frac{BIO1}{10})^2-85.6399\frac{BIO11}{10}-0.1171BIO12+0.4483BIO15$&43&0.1975&3387&2.72&479.882\\
$(9)AGB=2.546\textsuperscript{e+04}-1.337\textsuperscript{e+02}|Lat|-1.653\textsuperscript{e+03}\frac{BIO1}{10}+3.743\textsuperscript{e+01}(\frac{BIO1}{10})^2-2.499\textsuperscript{e+02}\frac{BIO11}{10}-9.722\textsuperscript{e-02}BIO12-2.508\textsuperscript{e+00}BIO15+2.422\textsuperscript{e-02}EVI$&40&0.3627&3369&2.60&447.478\\
$(10)AGB=-1916.5321+7.3424BIO9+0.1126BIO17$&43&0.1456&3607&4.58&479.110\\
$(11)AGB=-1.693\textsuperscript{e+03}-2.897\textsuperscript{e+01}Lat+7.567\textsuperscript{e+00}BIO9-4.108\textsuperscript{e-02}BIO17$&43&0.2072&3346&4.66&476.801\\
$(12)AGB=-2.391\textsuperscript{e+03}-9.020\textsuperscript{e+00}Lat+9.087\textsuperscript{e+00}BIO9+1.105\textsuperscript{e-01}BIO17+1.695\textsuperscript{e-02}EVI$&43&0.1898&3514&3.284&446.756\\
$(13)AGB=-1.855\textsuperscript{e+03}-2.390\textsuperscript{e+01}Lat+7.809\textsuperscript{e+00}1BIO9+9.615\textsuperscript{e-03}EVI$&40&0.2001&3469&4.25&445.371\\
$(14)AGB=-3.232\textsuperscript{e+02}+1.499\textsuperscript{e+00}BIO9+5.1442EVI$&40&-0.01318&4394&0.75&453.920\\
$(15)AGB=-1860.211+7.958BIO9-22.944Lat$&43&0.2225&3282&7.01&475.052\\
$(16)AGB=-423.235+1.943BIO9$&43&0.01697&4149&1.72&484.202\\
$(17)AGB=-1.1408\textsuperscript{e+03}-9.370\textsuperscript{e+00}BIO11+3.327\textsuperscript{e-02}BIO16+1.348\textsuperscript{e+01}BIO9+1.065\textsuperscript{e-02}EVI$&40&0.2082&3434&3.56&445.835\\
$(18)AGB=-2.670\textsuperscript{e+03}+9.671\textsuperscript{e+00}BIO11+1.008\textsuperscript{e-01}BIO16+2.298\textsuperscript{e-02}EVI$&40&0.06889&4038&1.96&451.446\\
$(19)AGB=-822.9927+3.0227BIO11+0.2433BIO16-0.4077BIO17$&43&0.04791&4019&1.70&484.676\\
$(20)AGB=-835.18954-20.28373BIO11+0.02986BIO16+14.30146BIO9+8.635535BIO1+0.01895EVI$&40&0.2143&3408&3.13&446.366\\
$(21)AGB=3.451\textsuperscript{e+04}-2.302\textsuperscript{e+02}\frac{BIO11}{10}-8.086\textsuperscript{e-03}BIO16+2.071\textsuperscript{e+02}\frac{BIO9}{10}2.549\textsuperscript{e+03}\frac{BIO1}{10}+4.777\textsuperscript{e+01}(\frac{BIO1}{10})^2+2.018\textsuperscript{e-02}EVI$&40&0.2309&3336&2.95&446.319\\
$(22)AGB=-9.327\textsuperscript{e+02}+1.846\textsuperscript{e-03}BIO10^2+1.132\textsuperscript{e-02}BIO11^2+1.476\textsuperscript{e-05}BIO16^2+5.747\textsuperscript{e-05}BIO17^2+2.556\textsuperscript{e-06}EVI^2$&40&0.04177&4518&0.69&457.651\\
$(23)\log{AGB}=-249.0196+23.8766\log{BIO10}+17.2434\log{BIO11}+1.3926\log{BIO16}+0.2169\log{BIO17}+1.5243\log{EVI}$&40&0.1954&0.614&2.89&101.484\\
$(24)AGB=-17786.59+1487.86\log{BIO10}+1428.78\log{BIO11}+115.81\log{BIO16}+12.94\log {BIO17}+87.21\log{EVI}$&40&0.08968&3948&1.77&452.256\\
$(25)\log{AGB}=-191.3654+32.0857\log{BIO9}+1.1316\log{BIO16}+1.0113 \log{EVI}$&40&0.3028&0.532&6.65&94.038\\
$(26)\log{AGB}=-94.7756+21.9228\log{BIO9}-3.2190\log{BIO16}+0.8363\log{EVI}-1.1157|Lat|$&40&0.3586&0.489&6.45&91.573\\
$(27)\log{AGB}=-18.7623+39.9688\log{BIO9} -3.0771\log{BIO16}+0.7138\log{EVI}-0.8834|Lat|-32.0563\log{BIO11}$&40&0.353&0.493&5.26&92.761\\ 
$(28)AGB=2071.2-569777.6\frac{1}{BIO9}+20516.4\frac{1}{BIO16}-333815.1\frac{1}{EVI}+1377.2\frac{1}{|Lat|}$&40&0.2631&3196&4.48&442.959\\
$(29)\frac{1}{AGB}=9.895\textsuperscript{e-01}-2.836\textsuperscript{e-03}BIO9-4.386\textsuperscript{e-05}BIO16-1.638\textsuperscript{e-05}EVI-9.419\textsuperscript{e-03}|Lat|$&40&0.1415&0.0014&2.61&-143.157\\
$(30)\frac{1}{AGB}=-0.4451+154.8629\frac{1}{BIO9}-49.9774\frac{1}{BIO16}+388.4439\frac{1}{EVI}-0.8805\frac{1}{|Lat|}$&40&0.5587&0.0007&13.34&-169.773\\
$(31)\log{AGB}=-68.661+21.023\log{BIO9}-5.397\log{BIO16}+1.842\log{EVI}-11.790\log{|Lat|}$&40&0.4507&0.419&9.00&85.375\\
$(32)\log{AGB}=-2.889\textsuperscript{e+01}+1.217\textsuperscript{e-01}\log{BIO9}+4.858\textsuperscript{e-04}\log{BIO16}+2.457\textsuperscript{e-04}\log{EVI}-1.613\textsuperscript{e-01}|Lat|$&40&0.2641&0.561&4.50&97.073\\
$(33)AGB=-6880.48+1646.40\log{BIO9}-262.05\log{BIO16}+98.26\log{EVI}-639.37\log{|Lat|}$&40&0.2671&3179&4.55&442.745\\
$(34)AGB=-3707.820+256.857\sqrt{BIO9}-1.560\sqrt{BIO16}+1.600\sqrt{EVI}-166.952\sqrt{|Lat|}$&40&0.1981&3478&3.41&446.345\\
$(35)\sqrt{AGB}=-1.202\textsuperscript{e+02}+4.813\textsuperscript{e-01}BIO9-1.923\textsuperscript{e-03}BIO16+8.131\textsuperscript{e-04}EVI-7.431\textsuperscript{e-01}|Lat|$&40&0.2531&8.62&4.30&206.338\\
$(36)\log{AGB}=32.568-8256.480\frac{1}{BIO9}+572.760\frac{1}{BIO16}-6457.220\frac{1}{EVI}+21.747\frac{1}{|Lat|}$&40&0.4675&0.406&9.56& 84.130\\ 
$(37)AGB=-1.855\textsuperscript{e+03}+7.809\textsuperscript{e+00}BIO9+9.615\textsuperscript{e-03}EVI-2.390\textsuperscript{e+01}|Lat|$&40&0.2001&3469&4.25&445.371\\
$(38)\log{AGB}=-183.9219+32.6554\log{BIO9}+1.2009\log{EVI}-2.2817\log{|Lat|}$&40&0.3572&0.490&8.22&90.790\\
$(39)\log{AGB}=-2.532\textsuperscript{e+01}+1.156\textsuperscript{e-01}BIO9+1.906\textsuperscript{e-04}EVI-3.007\textsuperscript{e-01}|Lat|$&40&0.2807&0.549&6.07&95.288\\
$(40)AGB=-12476.98+2211.21\log{BIO9}+67.12\log{EVI}-177.67\log{|Lat|}$&40&0.2423&3286&5.16&443.200\\ 
$(41)AGB=-3980.6149+264.1664\sqrt{BIO9}+1.7156|sqrt{EVI}-132.2929\sqrt{|Lat|}$&40&0.2199&3383&4.66&444.367\\
$(42)\sqrt{AGB}=-1.061\textsuperscript{e+02}+4.570\textsuperscript{e-01}BIO9+5.950\textsuperscript{e-04}EVI-1.295\textsuperscript{e+00}|Lat|$&40&0.2699&8.430&5.80&204.556\\
$(43)\log{AGB}=36.254-8845.587\frac{1}{BIO23}-5303.932\frac{1}{EVI}+15.133\frac{1}{|Lat|}$&40&0.4507&0.419&11.67&84.502\\
$(44)\log{AGB}=12.977-2107.057\frac{1}{BIO9}-3371.758\frac{1}{EVI}$ &40&0.1931&0.615&5.67&98.980\\
$(45)\log{AGB}=-751.4362+8.8199\log{BIO9}+0.7639\log{EVI}$&40&0.1312&0.6626&3.94&101.936\\
$(46)\log{AGB}=-6.0469510+0.0361823BIO9+0.0001344EVI$&40&0.08879&0.695&2.90&103.843\\
$(47)\sqrt{AGB}=-2.311\textsuperscript{e+01}+1.151\textsuperscript{e-01}BIO9+3.528\textsuperscript{e-04}EVI$&40&0.03062&11.188&1.62&214.990\\   
$(48)\log{AGB}=27.758--5876.246\frac{1}{BIO9}-3042.594\frac{1}{BIO16}-610.758\frac{1}{EVI}$ &40&0.2675&0.559&5.75&96.015\\

@@

\clearpage
